Exploring Hillary Clinton's Emails\thanks{STATS 601 final project.}

### 2016-04-18 paper/paper.tex
Fleshing out paper outline.

\documentclass{article}

@@

@@

\section{Data Summary}

\section{MDS}

\section{Spectral Clustering}

\section{TM Background/Estimation}

\section{Interpreting Topics/Model Selection}

\section{Types of Topics}

\section{Interesting Topics}

\section{Who Says What/Multinomial Regression}

>>>>

\documentclass[12pt]{article}

% General
\usepackage[round]{natbib}
\usepackage{setspace}
\usepackage{geometry}
\usepackage[section]{placeins}
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx}
\usepackage{color}
\usepackage{titlesec}
\usepackage[page]{appendix}
\usepackage{enumerate}

% Tables/Figures
\usepackage{lscape}
\usepackage{booktabs}
\usepackage{rotating}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}

% Math
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{dsfont}

% \doublespacing
\onehalfspacing
% \singlespacing

% \numberwithin{equation}{section}

\geometry{paper=letterpaper, margin=1in}
\captionsetup{font=small}

% Code
\usepackage{textcomp}
\usepackage{sourcecodepro}
\usepackage{listings}
\definecolor{commentgrey}{gray}{0.45}
\definecolor{backgray}{gray}{0.96}
\lstset{
  basicstyle=\footnotesize\ttfamily, keywordstyle=\footnotesize,
  backgroundcolor=\color{backgray}, commentstyle=\color{commentgrey},
  frame=single, rulecolor=\color{backgray}, showstringspaces=false,
  breakatwhitespace=true, breaklines=true, upquote=true,
  numbers=left, numberstyle=\footnotesize\color{commentgrey}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% User-defined LaTeX commands
\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator{\Cov}{Cov}
\DeclareMathOperator{\Corr}{Corr}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
\newcommand*{\expp}[1]{\exp\left(#1\right)}
\newcommand*{\foralls}{\ \forall \ }
\newcommand*{\st}{\text{ s.t. }}
\newcommand*{\E}{\mathbb E}
\newcommand*{\R}{\mathbb R}
\newcommand*{\I}{\mathds{1}}
\newcommand*{\Prob}{\mathbb P}
\newcommand*{\convas}[1]{\xrightarrow{#1}}
\newcommand*{\conv}{\convas{}}
\newcommand*{\cond}{\;\ifnum\currentgrouptype=16 \middle\fi|\;}
\newcommand*{\defeq}{%
  \mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily def}}}{=}}}
\newcommand*{\notorth}{\ensuremath{\perp\!\!\!\!\!\!\diagup\!\!\!\!\!\!\perp}}
\newcommand*{\orth}{\ensuremath{\perp\!\!\!\perp}}
\newcommand*{\evalat}{\,\big\rvert}
\newcommand*{\dif}{\,d}
\newcommand*{\difto}[1]{\,d^#1}
\newcommand*{\difbot}[1]{\frac{d}{d#1}}
\newcommand*{\partialbot}[1]{\frac{\partial}{\partial#1}}
\newcommand*{\m}[1]{\textbf{#1}}
\newcommand*{\bmath}[1]{\boldsymbol{#1}}

\newcommand*{\yestag}{\addtocounter{equation}{1}\tag{\theequation}}
\newcommand*{\notaligned}[1]{\noalign{$\displaystyle #1$}}
\newcommand*{\ttilde}{{\raise.17ex\hbox{$\scriptstyle\sim$}}}

\makeatletter
\newsavebox{\mybox}\newsavebox{\mysim}
\newcommand*{\distas}[1]{%
  \savebox{\mybox}{\hbox{\kern3pt$\scriptstyle#1$\kern3pt}}%
  \savebox{\mysim}{\hbox{$\sim$}}%
  \mathbin{\overset{#1}{\kern\z@\resizebox{\wd\mybox}{\ht\mysim}{$\sim$}}}%
}
\makeatother
\newcommand*{\dist}{\sim}
\newcommand*{\distiid}{\distas{\text{i.i.d}}}

\makeatletter
\def\moverlay{\mathpalette\mov@rlay}
\def\mov@rlay#1#2{\leavevmode\vtop{%
   \baselineskip\z@skip \lineskiplimit-\maxdimen
   \ialign{\hfil$\m@th#1##$\hfil\cr#2\crcr}}}
\newcommand*{\charfusion}[3][\mathord]{
  #1{\ifx#1\mathop\vphantom{#2}\fi\mathpalette\mov@rlay{#2\cr#3}}
  \ifx#1\mathop\expandafter\displaylimits\fi}
\makeatother
\newcommand*{\cupdot}{\charfusion[\mathbin]{\cup}{\cdot}}
\newcommand*{\bigcupdot}{\charfusion[\mathop]{\bigcup}{\cdot}}

\newcommand*{\mt}[1]{\text{\normalfont #1}}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{theorem*}{Theorem}
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}{Lemma}[section]

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{definition*}{Definition}
\newtheorem{example}{Example}[section]
\newtheorem*{properties}{Properties}

\newtheoremstyle{algodesc}{}{}{}{}{\bfseries}{.}{ }{}%
\theoremstyle{algodesc}
\newtheorem{algodesc}{Algorithm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{Exploring Hillary Clinton's Emails\thanks{STATS 601 final project.}}
\author{
    Leland Bybee, Roger Fan, Ryan Vaughn
}
\date{\today}

\maketitle

@@

\section{Data}

\section{Visualization}
Motivation, cosine distance

\subsection{Multidimensional Scaling}

\subsection{Spectral Clustering}

\section{Topic Modeling}
Include model description, estimation strategy, and model selection.

\subsection{Interpreting Topics}
Include ``grunt work'' of interpreting topics, topic frequency

\subsection{Types of Topics}
Talk about structural, common word, and semantic topics, including ``interesting'' vs. ``non-interesting'' topics, discuss strengths of model in comparison to MDS

\subsection{Topic Analysis}
Analyze some specific topics, compare use over time and how it correlates with related events

\section{Email Sender Prediction}
Talk about the who says what table

\subsection{Multinomial Logistic Regression}
Quickly describe model and discuss results
